An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-16 poly-embed-journal/poly-embed-journal.tex
added indexing to clarify something

\section{``Book chapter'' approach}
\subsection*{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $w\in\reals^\Y_+, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} - b \geq 0\}$ be the closed halfspace defined by $(w,b)$, where $d = |\Y| +1$.
	Abusing notation, we sometimes write $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$.\jessie{Is notation clear?}
\end{definition}
Additionally, we sometimes let $H_y^+ := H_{e_y}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$.
	Again, we let $H_v := H_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$. 
\end{definition}

\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}$ presented in the form $P = \cap \H$.
%	\begin{equation*}
%	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
%	\end{equation*}
\end{definition}
\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
\begin{definition}[Face, facet]
	Let $P \subseteq \reals^d$ be a convex polytope.
	A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
	A \emph{face} of the polytope $P$ is any set of the form
	\begin{equation*}
	F = P \cap H_{(w,b)}~,~
	\end{equation*}
	for any valid halfspace $H^+_{(w,b)}$.
	The dimension of a face is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
	A $(\dim(P) - 1)$-dimensional face is called a facet.
\end{definition}

@@

Projections to the positive orthant
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item 
\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = \{x \in \reals^d \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V$ such that $x \in F_V$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this.}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

@@

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
\item We once again have $G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\item Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\item Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
\item Claim: for all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{itemize}

>>>>

\section{``Book chapter'' approach}
\subsection*{Definitions and preliminaries}
\begin{definition}[Closed halfspace]
	For any $w\in\reals^\Y_+, b \in \reals$, let $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} - b \geq 0\}$ be the closed halfspace defined by $(w,b)$, where $d = |\Y| +1$.
	Abusing notation, we sometimes write $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^\Y_+$.\jessie{Is notation clear?}
\end{definition}
Additionally, denote $H_y^+ := H_{([e_y; -1], 0)}^+$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\begin{definition}[Hyperplane]
	For any $(w,b)\in\reals^\Y_+ \times \reals$, let $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} - b = 0\}$ be the hyperplane generated by $(w,b)$, and the boundary of $H^+_{(w,b)}$.
	Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$. 
\end{definition}

\begin{definition}[Polyhedron - halfspace representation\jessie{Ziegler page 28}]
	An \emph{polyhedron} $P$ describes an intersection of a finite set of closed halfspaces $\H = \{H^+_{(w_i,b_i)}\}_{i=1}^k$ presented in the form $P = \cap \H$.
%	\begin{equation*}
%	P = P(A,z) = \{x \in \reals^d \mid Ax \leq z\} \qquad \textrm{ for some } A \in \reals^{m \times d}, z \in \reals^m~.~
%	\end{equation*}
\end{definition}
%\jessie{Comment the above out, and define as a finite intersection of closed halfspaces}
\begin{definition}[Face, facet]
	Let $P \subseteq \reals^d$ be a convex polytope.
	A halfspace $H^+_{(w,b)}$ is \emph{valid} for $P$ if $P \subseteq H^+_{(w,b)}$.
	%A linear inequality $\inprod{w}{x} \geq b$ is \emph{valid} for $P$ if it is satisfied for all $x \in P$.
	A \emph{face} $F_{(w,b)}$ of the polytope $P$ is any set of the form
	\begin{equation*}
	F_{(w,b)} = P \cap H_{(w,b)}~,~
	\end{equation*}
	for any valid halfspace $H^+_{(w,b)}$.
	The dimension of a face $F$ is the dimension of its affine hull $\dim(F) := \dim(\affhull(F))$.
	A $(\dim(P) - 1)$-dimensional face is called a facet.
\end{definition}

@@

Projections to the positive orthant
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item 
\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V$ such that $x \in F_V$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this.}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

@@

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\hat\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\hat \V} = \{H_v^+ \mid v\in\hat\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\hat \V}$.
\item 
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\end{claim}
\item 
\begin{claim}
	Argue that $\H_\V \subseteq \H$, since $\H_\Y \cup \H_\V$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{claim}
\item 
\begin{corollary}
	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V$ (without duplicates).
\end{corollary}
\item 
\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V = L(\R^*)$. \raf{(1)}
\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{itemize}
